---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# NHSmod11

<span style="color:red"> ***This package has not yet been code reviewed and is not yet used in production. Buyer beware***  </span>

<!-- badges: start -->
<!-- badges: end -->

Minimal and efficient package to validate that a given NHS number passes the
modulo 11 check
(see https://www.datadictionary.nhs.uk/attributes/nhs_number.html for details).


## Installation

The development version, which this documentation refers to, can be installed
from the internal GitLab instance via

```
if (!require(remotes)) install.packages("remotes")

remotes::install_git(
    "https://gitlab.phe.gov.uk/Timothy.Taylor/NHSmod11.git",
    subdir="pkg",
    dependencies = TRUE,
    build_vignettes = TRUE
)
```

## Example

```{r example}
library(NHSmod11)

# all of these should be valid
dat1 <- c("5390502108", "2788584652", "3510670485", "4001126419", "5309741852")
is_valid_mod11(dat1)

# these are numeric versions of above and should therefore also be valid
dat2 <- c(5390502108, 2788584652, 3510670485, 4001126419, 5309741852)
is_valid_mod11(dat2)

# these should all be invalid
dat3 <- c("5390502107", "2788584651", "3510670484", "4001126418", NA_character_)
is_valid_mod11(dat3)
```

## Getting help online

Bug reports and feature requests should be posted on *gitlab* using the
[*issue* system](https://gitlab.phe.gov.uk/Timothy.Taylor/NHSmod11/issues).
